### 2016-03-14 paper/result_stereo.tex
yasu

Figure~\ref{fig:stereo_global} compares the converegence rate of the
competing methods. Note that we define the energy of a multi-threading
system to be the energy of the best solution found so far.
%
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/stereo_global.png}
 \caption{Energy plots for the stereo problem. The energy is in the
 log scale. For a multi-threading algorithm, the energy at any given
 moment is defined to be the best solution so far.} \label{fig:stereo_global}
\end{figure}
%
One unusual outcome is that Sequential Alpha Expansion and Parallel
Alpha Expansion (PAE) have the same convergence speed, indicating that
the stereo problem is a very easy one. This is well known in a community
and this fact was rather expected. Our approaches with multi-way fusion
(SF-SS or SF) are the slowest kind, because the TRW-S for multi-way
fusion is slower than multiple Alpha Expansion steps, and this stereo
problem is too easy to gain benefits through mulit-way fusion.
%
%Another interesting observation is that the Hierarchical Fusion can
%achieve good energy only when they merge solutions at the top of the
%tree.
%
%  both PAE and SF-MF converge faster
% than sequential method. However, since fusing solutions with multiple
% labels by QPBO is slower than a single $\alpha$-expansion, PAE method
%
% Finally, the line of hierarchy fusion only makes
% jump when fusing on root node of the tree. This is because any fusion
% step on non-root nodes only have partial label information.
%We recoreded both single thread energy and system energy against
%time.
%
Figure \ref{fig:stereo_threads} shows the energy plot per thread
for SF-MF (ours) and PAE. The graph for PAE again confirms that the
stereo is an easy problem, because all the threads are quickly
converging to a solution before the final sequential fusion.
%shows the per-thread energy
%minimization process in SF-MF and PAE. The per-thread energy in SF-MF
%architecture decreases more uniformly than that of PAE. In the
%scenario where we need to query the best solution so far before the
%whole optimization converges, SF-MF architecture is a better choice.
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/stereo_threads.png}
  \caption{\yasu{Put a text in the figures showing which one is
  SF-MF(ours) and which one is parallel alpha expansion} Per thread
  energy. The left and right figures show the energy minimization
  process on each working thread of our method in SF-MF configuration
  and parallel $\alpha$-expansion method, respectively. The energy is in
  $\log$ scale} \label{fig:stereo_threads}
\end{figure}

>>>>

Figure~\ref{fig:stereo_global} compares the converegence rate of the
competing methods. Note that we define the energy of a multi-threading
system to be the energy of the best solution found so far.
%
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/stereo_global.png}
 \caption{Energy plots for the stereo problem. The energy is in the log
 scale. For a multi-threading algorithm, the energy at a given moment is
 defined to be the best solution so far.} \label{fig:stereo_global}
\end{figure}
%
One unusual outcome is that Sequential Alpha Expansion and Parallel
Alpha Expansion (PAE) have the same convergence speed, indicating that
the stereo problem is a very easy one. This is well known in a community
and this fact was rather expected. Our approaches with multi-way fusion
(SF-SS or SF) are the slowest kind, because the TRW-S for multi-way
fusion is slower than multiple Alpha Expansion steps, and this stereo
problem is too easy to gain benefits through mulit-way fusion.
%
%Another interesting observation is that the Hierarchical Fusion can
%achieve good energy only when they merge solutions at the top of the
%tree.
%
%  both PAE and SF-MF converge faster
% than sequential method. However, since fusing solutions with multiple
% labels by QPBO is slower than a single $\alpha$-expansion, PAE method
%
% Finally, the line of hierarchy fusion only makes
% jump when fusing on root node of the tree. This is because any fusion
% step on non-root nodes only have partial label information.
%We recoreded both single thread energy and system energy against
%time.
%
Figure \ref{fig:stereo_threads} shows the energy plot per thread
for SF-MF (ours) and PAE. The graph for PAE again confirms that the
stereo is an easy problem, because all the threads are quickly
converging to a solution before the final sequential fusion.
%shows the per-thread energy
%minimization process in SF-MF and PAE. The per-thread energy in SF-MF
%architecture decreases more uniformly than that of PAE. In the
%scenario where we need to query the best solution so far before the
%whole optimization converges, SF-MF architecture is a better choice.
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/stereo_threads.png}
  \caption{\yasu{Put a text in the figures showing which one is
  SF-MF(ours) and which one is parallel alpha expansion}
 Energy plots per thread for the stereo problem for SF-MF (left) and
 Parallel Alpha Expansion (right).
} \label{fig:stereo_threads}
\end{figure}
